### 2012-06-21 inst/examples/Sethi.Rmd
Sethi with uniform noise, logistic

`ro cache=FALSE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE or`

``` {r  echo=FALSE, cache=FALSE }
opts_knit$set(upload.fun = socialR::flickr.url)
orig = getOptions("device")
options(device = function(width = 5, height = 5) {
    pdf(NULL, width = width, height = height)
})
knitcitations::cleanbib()
````

@@

``` {r sethiplots, dependson="runall"}
policy <- data.frame(stock = x_grid, value = opt$D[,1])
ggplot(policy) + 
  geom_point(aes(stock, stock-x_grid[value], color=variable)) + 
	geom_smooth(aes(stock, stock-x_grid[value])) + ylab("escapement")

ggplot(policy) + 
  geom_point(aes(stock, x_grid[value], color=variable)) 
	geom_smooth(aes(stock, x_grid[value], color=variable)) + ylab("harvest")

value <- data.frame(stock = x_grid, value=opt$V)
ggplot(value) + 
  geom_point(aes(stock, value, color=variable)) +
  geom_smooth(aes(stock, value, color=variable)) +
  ylab("Net Present Value")
````

>>>>

`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache.path="Sethi/" or`

``` {r  echo=FALSE, cache=FALSE }
opts_knit$set(upload.fun = socialR::flickr.url)
orig = getOption("device")
options(device = function(width = 5, height = 5) {
    pdf(NULL, width = width, height = height)
})
knitcitations::cleanbib()
````

@@

``` {r sethiplots}
policy <- data.frame(stock = x_grid, value = opt$D[,1])
ggplot(policy) + 
  geom_point(aes(stock, stock-x_grid[value])) + 
	geom_smooth(aes(stock, stock-x_grid[value])) + ylab("escapement")

ggplot(policy) + 
  geom_point(aes(stock, x_grid[value])) + 
	geom_smooth(aes(stock, x_grid[value])) + ylab("harvest")

value <- data.frame(stock = x_grid, value=opt$V)
ggplot(value) + 
  geom_point(aes(stock, value)) +
  geom_smooth(aes(stock, value)) +
  ylab("Net Present Value")
````
